\chapter{Battle at the Mountain pass}

It was early morning in a mountain pass in Henan during the Xianbei ruled Northern Wei dynasty. The sun has just risen over the mountain tops, filling the sky with a seemingly orange light. The blue sky was clear with almost no clouds visible as far as the eyes can see. On the mountain passes' high hills and steep cliffs grew small batches of grass, small bushes, and trees of different kind.
A rooster could be heard from a distant, probably from a small village somewhere in this mountain area where the people are getting up early, and preparing for work. Everything seems to be peaceful, with life moving on as normal.

Along the mountain pass leaped a small road made of sand. On one side of the road are walls, made up by the cliffs. The other side were the edge of the cliff, one hast to be careful not to fall down from the road. There were occasional plateaus, suited for resting when for the travelling sales caravan, smaller armies, and other travelling parties. On one of these plateaus grew tree by the cliff side. Under the tree slept a man.

The man was dressed in a vest made out of tiger pelt. He's hair were dark and long, like many other asians. He wore a headband around the forhead, with the rest of the hair loose and resting on he's shoulders. He had little facial hair, and he's cheek bones had very visible, sharp features. By he's side were a broad sword, a bow, and a quiv with some arrows in it.

Apart from the singing birds, and some bugs making noice on the trees and inside the bushes, another sound can be heard. IT was a rumbling sound the echoed throughout the mountain pass. The sound were not strong, but enough to wake up the resting fellow below the trees from he's sweet dreams. He strechted he's arms on both directions and yawned. He stood up, and dusted of he's pants from the sand, and thought to himself "Who woke me up from my beauty sleep".

He sat down on he's knees, and put he's ears to the ground. The sound became much clearer. It was horse hoves, and quite a number of them. The man counted the numbers of horse hoves he could identify, about twenty of them, and they are moving swiftly towards he's position. The man stod up once again. He than took a big jump upwards, along the walls made of mountain cliff. He managed to grab a rock and gain some footing. And made another big jump and grabbed along a small branch of a tree that grew on the cliffs.

Once he gained a stable footing, he scouted with he's eyes towards the other side of the valley. Indeed, he's suspicions were true, there were a small division of riders approaching he's position. The small army was too far away to identify them, but he could get a pretty decent look at the standard they were carrying witch indicated that they were rourans. "Rouran scouts, maybe?" he thought to himself. "What business do they have scouting this mountain pass?".

He climbed down from the mountain and thought. "Whatever they are up to, what do I care?" He thought. "Though they might be up to no good though, and I think I am really in need of some morning exercise. These scouts are here just in time". He picked up equipped himself with he's weapons, and counted the arrows inside the quiv. Ten arrows, not enough for taking out the whole division but it will do, he thought.

\newsect

The 20 Rouran scouts are moving swiftly through this narrow mountain pass. They were dressed beige in coloured cloth, a chest piece, and boots made of leather. There helmets were made of steel and leather with a white pelt along the edges. Every one them were equipped with a slightly curved, sabre like broadsword by there side.

In front of the division rides there leader, and two other higher ranking offiers. One of them were holding the standards. All three of them wore capes. The leader wore a white cape, with a white and black stripped pelt around the edges, he also wore shoulder pads made of steel with wolf teeth. The other two officers wore red capes and simpler shoulder pads made of steel on only one shoulder.

An eagle could be heard shouting in the air.
"General, post eagle" shouted a soldier from behind. He pointed to wards sky in the direction of the cliff side. Indeed, a big message eagle can be seen flying towards them. The Rourans used eagles as carriers to transfer writtens messages. Over the years, it has become quite well practised among their people.
